\thispagestyle{plain}
	\section{REFERENCIAS BIBLIOGRÁFICAS}
		\begin{enumerate}
			
			\item 
			Batería de ion de litio. (2018, February 06). Retrieved February 18, 2018, from https://es.wikipedia.org/wiki/Bater%C3%ADa_de_ion_de_litio
			
			\item ENAC Caracterización de Medios Isotermos, NT-04 Rev. 3 Diciembre 2014.
			
			\item Margolis, M. (2013). Arduino cookbook. Sebastopol, CA: OReilly.
			
			\item Nielsen, J., \& Budiu, R. (n.d.). Mobile Usability.
			
			\item Nordic Semiconductor (2008). nRF24L01+ 
			Single Chip 2.4GHz Transceiver.
			
			\item S. K. (2014). Don't Make Me Think, Revisited: A Common Sense Approach to Web Usability (3rd ed., Voices That Matter). New Riders. 
			
			\item K. D. (2016, November 22). DS18B20 (digital temperature sensor) and Arduino. Retrieved February 05, 2018,
			\\from https://create.arduino.cc/projecthub/TheGadgetBoy/ds18b20-digital-temperature-sensor-and-arduino-9cc806
			
			\item 
			Slatkin, B. (2015). Effective Python: 59 specific ways to write better Python. Upper Saddle River, NJ: Addison-Wesley.
			
			\item General requirements for the competence of testing and calibration laboratories: (ISO/IEC 17025: 2005, IDT). (2005). Shah Alam, Selangor: SIRIM Berhad.
			
			\item Organización Panamericana de la Salud. Área de Tecnología y Prestación de Servicios
			de Salud. Unidad de Medicamentos Esenciales, Vacunas y Tecnologías en Salud.
			Manual de Mantenimientos para Equipos de Laboratorios. Washington, D.C. 2005.
			
			\item Openpyxl 2.5.0b1. (n.d.). Retrieved November 28, 2017, \\from https://pypi.python.org/pypi/openpyxl
			
			\item Pyserial 3.4. (n.d.). Retrieved November 28, 2017, \\from https://pypi.python.org/pypi/pyserial
			
			\item PyQt Class Reference. (n.d.). Retrieved November 28, 2017, \\from http://pyqt.sourceforge.net/Docs/PyQt4/classes.html
			
	 		\item Point, T. (2017, August 15). PyQt Tutorial. Retrieved November 28, 2017, \\from https://www.tutorialspoint.com/pyqt/index.htm
				
			\item What is Arduino? (n.d.). Retrieved November 28, 2017, \\from https://www.arduino.cc/en/Guide/Introduction
			
			
						
			
		\end{enumerate}